My title

### 2024-03-11 paper/paper.qmd
add subsections
added posterior predictive check for model result

library(tidyverse)
library(palmerpenguins)
library(here)
library(rstanarm)
library(modelsummary)
library(ggplot2)
```

@@

@@

@@

Talk more about it.

And also planes (@fig-planes). (You can change the height and width, but don't worry about doing that until you have finished every other aspect of the paper - Quarto will try to make it look nice and the defaults usually work well once you have enough text.)

```{r}
#| label: fig-planes
#| fig-cap: Relationship between wing length and width
#| echo: false
#| warning: false
#| message: false

# analysis_data <- read_csv(here::here("data/analysis_data/analysis_data.csv"))
# 
# analysis_data |> 
#   ggplot(aes(x = width, y = length)) +
#   geom_point(alpha = 0.8) +
#   theme_minimal() +
#   labs(x = "Wing width (mm)",
#        y = "Wing length (mm)")
```

Talk way more about it.

@@

>>>>

library(tidyverse)
library(palmerpenguins)
library(here)
library(rstanarm)
library(modelsummary)
library(ggplot2)
library(knitr)
library(marginaleffects)
```

@@

## Estimand

@@

## Data Measurement

## Summary Statistics

@@

@@

```
```{r}
# We could use posterior predictive checks, introduced in Section 12.4, to show that the logistic regression approach is a good choice for this circumstance.

pp_check(political_preferences1) +
  theme(legend.position = "bottom")
```
```{r}

# marginal effect -- ?

slopes(political_preferences1) |>
  summary() |>
  select(-term) |>
  kable(
    col.names = c("Compare department", "Estimate", "2.5%", "97.5%"),
    digits = 2, booktabs = TRUE, linesep = ""
  )
```
